# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
data0 <- read.csv("activity.csv",
                  colClasses = c("numeric", "character", "numeric"))
data1 <- data0[complete.cases(data0),]
```


## What is mean total number of steps taken per day?
Histogram of the total number of steps taken each day:
```{r}
result1 <- lapply(split(data1,data1$date),function(d){sum(d$step)}) 
result1 <- unlist(result1)
hist(result1, main = "Histogram of the total number of steps taken each day")
rug(result1)
```
Mean:
```{r}
mean(result1)
```
Median:
```{r}
median(result1)
```
  
## What is the average daily activity pattern?
```{r}
ts_data <- tapply(data1$steps, data1$interval, mean)
plot(row.names(ts_data), 
     ts_data, 
     type = "l",
     xlab = "5-min interval", 
     ylab = "Average across all Days", 
     main = "Average number of steps taken", 
     col = "blue")

```
  
The interval that contains the max. number of steps:
```{r}
names(which.max(ts_data))
```
  
## Imputing missing values

1.Total number of missing values on the dataset(i.e. total number of the rows with NAs)
```{r}
nrow(data0) - nrow(data1)
```
  
Fill in the missing values with the mean of that 5-min interval
```{r}
StepsAverage <- aggregate(steps ~ interval, data = data0, FUN = mean)
fillNA <- numeric()
for (i in 1:nrow(data0)) {
    obs <- data0[i, ]
    if (is.na(obs$steps)) {
        steps <- subset(StepsAverage, interval == obs$interval)$steps
    } else {
        steps <- obs$steps
    }
    fillNA <- c(fillNA, steps)
}
```
  
New dataset:
```{r}
data_new <- data0
data_new$steps <- fillNA
```

Histogram of the new dataset:
```{r}
histdata <- data_new[complete.cases(data_new),]
result2 <- lapply(split(data_new,data_new$date),function(d){sum(d$step)}) 
result2 <- unlist(result2)
hist(result2, main = "Histogram of the total number of steps taken each day")
rug(result2)
```
  
Mean:
```{r}
mean(result2)
```
Median:
```{r}
median(result2)
```
  
Result: the median is different by 1.

## Are there differences in activity patterns between weekdays and weekends?
